%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author : Feliks Kulikou, Tomas Polasek (template)
% Description : First exercise in the Introduction to Game Development course.
%   It deals with an analysis of a selected title from the point of its genre, 
%   style, and mechanics.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,english]{article}

\usepackage[left=2.50cm,right=2.50cm,top=1.50cm,bottom=2.50cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\newcommand{\ph}[1]{\textit{[#1]}}

\title{%
Analysis of Mechanics%
}
\author{%
Feliks Kulikou (xkulikf00)%
}
\date{8.10.2025}

\begin{document}

\maketitle
\thispagestyle{empty}

{%
\large

\begin{itemize}

\item[] \textbf{Title:} \ph{Ghost of Tsushima}

\item[] \textbf{Released:} \ph{2020}

\item[] \textbf{Author:} \ph{Sucker Punch Productions / Sony Interactive Entertainment}

\item[] \textbf{Primary Genre:} \ph{Action-adventure}

\item[] \textbf{Secondary Genre:} \ph{RPG, Open world, Stealth, Slasher}

\item[] \textbf{Style:} \ph{Jidaigeki, Cinematic}

\end{itemize}

}

\section*{\centering Analysis}

\section{Core gameplay}

The main gameplay involves traveling across Tsushima Island, completing quests, and fighting Mongol invaders or local bandits.

The action aspect features a well-crafted combat system requiring quick assessment and proper reactions:

1. Combat Mechanics. Several "stances" give advantages against specific enemy types. Light attacks are quick with moderate damage; heavy attacks are slow but stagger enemies with the correct stance and deal heavy damage. Players can block basic attacks and parry both basic and (late-game) special unblockable attacks (indicated by a white or red weapon glow). Successful parries stagger enemies and deal damage.

2. Ranged Weapons. Short bow draws quickly with short range and moderate damage; long bow draws slowly with long range and heavy damage. Each has different arrow types. Throwable weapons enable stealth kills or provide combat support.

3. Stealth System. Often required in quests. Tall grass hides the player from enemies. Stealth assassinations only succeed unseen, and bodies must be hidden to avoid raising alarms.

Adventure component involves completing the main story, optional side quests, and discovering points of interest to level up and unlock abilities. Points of interest are either directly accessible or feature small challenges like parkour sections or following foxes.

Movement is a cornerstone: travel on foot or horseback (summoned by button). Horses have a fear meter - if damaged or scared, they throw the player off, leaving them stunned. Parkour system for vertical/horizontal traversal, complemented by a grappling hook obtained during mid-game. Instead of a mini-map, players navigate by summoning "wind" that shows direction to selected objectives.

\section{Secondary genres}

RPG elements include leveling, skill trees, and gathering items for upgrades. Merchants and craftsmen in settlements upgrade gear for resources. RPG elements provide progression depth through character upgrades and gear customization, which complements the core gameplay.
Open-world with zone availability based on story progress. Fast travel is available, what gives player some comfort while traveling.

\section{Visual style}

Cinematic landscapes create the atmosphere of samurai-era Japan, romanticizing the period and honoring old samurai films. The cinematic visual style enhances the player's immersion in the game.

\end{document}
